### 2022-01-14 src-latex/parts/60-results.tex
Table 2 metrics

\begin{table}[!h]
\caption{Experimental results of the NER models performances when trained on varying numbers of examples.}
\centering
\begin{tabular}[t]{lrcccccccc}
 & Trainset size & 49 & 99 & 199 & 398 & 796 & 1593 & 3186 & 6373\\
 & \% & 0.8 & 1.5 & 3.1 & 6.2 & 12.5 & 25 & 50 & 100\\
\midrule[1pt]\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1}} & SpaCy NER & 0.87 & 0.89 & 0.90 & 0.92 & 0.92 & 0.93 & 0.93 & 0.94\\
& CamemBERT & 0.89 & 0.90 & 0.93 & 0.93 & 0.94 & 0.95 & 0.95 & 0.95\\
& CamemBERT.pretrained & 0.90 & 0.91 & 0.93 & 0.93 & 0.94 & 0.95 & 0.95 & 0.95\\
\cmidrule{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & SpaCy NER & 0.86 & 0.88 & 0.90 & 0.92 & 0.92 & 0.93 & 0.93 & 0.94\\
& CamemBERT & 0.87 & 0.88 & 0.91 & 0.93 & 0.93 & 0.95 & 0.94 & 0.96\\
& CamemBERT.pretrained & 0.88 & 0.90 & 0.92 & 0.93 & 0.93 & 0.94 & 0.94 & 0.95\\
\cmidrule{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & SpaCy NER & 0.89 & 0.90 & 0.91 & 0.92 & 0.92 & 0.93 & 0.93 & 0.93\\
& CamemBERT & 0.92 & 0.93 & 0.94 & 0.94 & 0.95 & 0.95 & 0.96 & 0.95\\
& CamemBERT.pretrained & 0.92 & 0.93 & 0.94 & 0.94 & 0.95 & 0.95 & 0.95 & 0.95\\
\end{tabular}
\end{table}

>>>>

\begin{table}[!h]
\caption{Experimental results of the NER models performances when trained on varying numbers of examples.}
\centering
\begin{tabular}[t]{lrcccccccc}
 & Trainset size & 49 & 99 & 199 & 398 & 796 & 1593 & 3186 & 6373\\
 & \% & 0.8 & 1.5 & 3.1 & 6.2 & 12.5 & 25 & 50 & 100\\
\midrule[1pt]\bottomrule
\multirow{3}{*}{\rotatebox{90}{F1}} & SpaCy NER & 87.0 & 89.0 & 90.3 & 91.9 & 92.1 & 92.8 & 93.2 & 93.6\\
& CamemBERT & 89.4 & 90.3 & 92.7 & 93.4 & 94.3 & 95.3 & 94.7 & 95.5\\
& CamemBERT.pretrained & 90.0 & 91.4 & 92.9 & 93.4 & 94.2 & 94.5 & 94.8 & 95.4\\
\cmidrule{1-10}
\multirow{3}{*}{\rotatebox{90}{Precision}} & SpaCy NER & 85.6 & 87.7 & 90.0 & 92.0 & 92.4 & 92.8 & 93.1 & 93.8\\
& CamemBERT & 87.3 & 88.1 & 91.4 & 93.0 & 93.4 & 95.4 & 93.8 & 95.8\\
& CamemBERT.pretrained & 87.9 & 89.8 & 91.6 & 92.7 & 93.4 & 94.0 & 94.1 & 95.4\\
\cmidrule{1-10}
\multirow{3}{*}{\rotatebox{90}{Recall}} & SpaCy NER & 88.6 & 90.4 & 90.7 & 91.7 & 91.9 & 92.8 & 93.3 & 93.3\\
& CamemBERT & 91.8 & 92.7 & 94.1 & 93.9 & 95.2 & 95.1 & 95.6 & 95.1\\
& CamemBERT.pretrained & 92.2 & 93.0 & 94.3 & 94.2 & 95.0 & 95.1 & 95.5 & 95.4\\
\end{tabular}
\end{table}
